Placeholder

### 2021-02-05 Paper_Histograms.Rmd
Added employment retro graph for combined samples

>>>>

```{r GLAD/EDGI NBR and RAMP retro employment}

dat.retro %>% 
  ggplot(aes(x = employment_prior_covid, fill = Sample_plot)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = COPINGpalette6) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Employment distribution of the retro cohorts",
       subtitle = paste("N =", dim(dat.retro)[1]),
       x = "",
       y = "") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank())
